\chapter{Analysis/Requirements}

\section{Analysis}
From background research, it was clear that despite there being many online music creation sites, there were not many applications which played back generated music in real-time and allowed user inputs to change how the music was created as it is generated. There was also a lack of collaborative experiences that were easily accessible to users with little musical experience.

From this, the functional and non-functional requirements can be defined.

\section{Requirements}

\subsection{Functional Requirements}

Site framework:
\begin{itemize}
    \item 
        Users should be able to create an account and login to the app using their credentials.
    \item 
        Users, logged in or not, can join an audio room, and each room should accommodate multiple users to be connected to it.
\end{itemize}

Synchronised functions:
\begin{itemize}
    \item 
        All changes to an audio room should occur in close to real-time.
    \item 
        Users should be able to adjust modifiers or parameters of the different tracks while they are generated and/or are playing.
    \item 
        Users should be able to hear audibly when they change a track’s parameters or modifiers in real time.
    \item 
        Changes made by one user should be reflected to all other connected users with negligible latency.
    \item 
        Each user should hear an identical audio output during a given session.
\end{itemize}

Audio tracks:
\begin{itemize}
    \item 
        There should be three audio tracks, each with its own panel where users can adjust the parameters and modifiers of each track. There will be an ambience mixer, a 16-step sequencer, and a panel with various instruments.
    \item 
        Users should be able to mix several ambient noises together to create a soundscape.
    \item 
        Users should be able to use the sequencer to create a looping drum pattern.
    \item 
        Users should be able to add instruments to the mix and alter how they sound using modifiers and parameters.
\end{itemize}

\subsection{Non-Functional Requirements}

Performance and reliability:
\begin{itemize}
    \item 
        The system should be able to send audio messages consistently and in time with the beat.
    \item 
        The time between a user adjusting a parameter or modifier and that change being synchronised with all other connected users should be minimised.
    \item 
        The system should be able to handle a large number of connected users to a room without significant latency or beat consistency problems.
\end{itemize}

Usability:
\begin{itemize}
    \item 
        The UI should be intuitive and clean so the user is not overwhelmed or confused.
    \item 
        The system should support multiple device sizes and resolutions to provide an accessible and consistent experience across platforms and screen sizes.
\end{itemize}

Deployment:
\begin{itemize}
    \item 
        The app should be fully deployed on a live site with all features working as intended
    \item 
        The deployed app should be stable and live without disruption.
\end{itemize}

Psychosocial:
\begin{itemize}
    \item 
        Users should feel connected to each other while they create music together in an audio room.
    \item 
        Users should feel relaxed and engaged in the music-making process.
\end{itemize}
